---
title: "Complete Analysis (short version)"
author: "Rajath Prabhakar"
date: "2024-04-01"
output:
  html_document: default
  pdf_document: default
---
```{r}
library(here)
library(DT)
```
```{r}
city <- "Atlanta"
date <- "2020-05-29"
```

```{r}
source(here("Functions", "06 - forecast_reddit().R"))
```

```{r}
atlanta_05292020 <- forecast_reddit(date = date, city = city)$projection
```

```{r}
atlanta_05292020
```

Missing values in mean_illness, illness7, illness14, illness21

Why missing values in those columns?

```{r}
city_training_data <- reddit_and_cases %>%
  filter(City == city) %>%
  mutate(illness7 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 7),
         illness14 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 14),
         illness21 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 21)) %>%
  filter(between(Date, as.Date(date) - 27, as.Date(date))) %>% 
  select(Date, City, MSA_Code, Daily_Cases7, mean_illness, illness7, illness14, illness21)
city_training_data
```

mean_illness - missing values from 05-19 to 05-24
illness7 - missing values from 05-26 to 05-29
illness14 - no missing values
illness21 - no missing values

How does this affect the model?

```{r}
city0_model <- lm(Daily_Cases7 ~ mean_illness + illness7 + illness14 + illness21, data = city_training_data)
city7_model <- lm(Daily_Cases7 ~ illness7 + illness14 + illness21, data = city_training_data)
city14_model <- lm(Daily_Cases7 ~ illness14 + illness21, data = city_training_data)
city21_model <- lm(Daily_Cases7 ~ illness21, data = city_training_data)
```

```{r}
city0_model_summary <- summary(city0_model)
city7_model_summary <- summary(city7_model)
city14_model_summary <- summary(city14_model)
city21_model_summary <- summary(city21_model)
```

```{r}
city0_model_summary
```

```{r}
city7_model_summary
```

```{r}
city14_model_summary
```

```{r}
city21_model_summary
```

No problems in training models. What about projections?

```{r}
city_projection_data <- reddit_and_cases %>% 
  filter(City == city) %>% 
  mutate(illness7 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 7),
         illness14 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 14),
         illness21 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 21)) %>%
  filter(between(Date, as.Date(date), as.Date(date) + 21))
```

```{r}
city_projection_data
```


```{r}
# Display data frame with pagination and search/filter feature
DT::datatable(city_projection_data, options = list(pageLength = 10))

```

Here no row has all 4 of the relevant columns for running the city0_model (illness7, illness14, illness21, mean_illness). Also for the city7_model, no row has all 3 of the relevant columns needed to run that model (illness7, illness14, illness21). 

```{r}
city_projection_data <- reddit_and_cases %>% 
  filter(City == city) %>% 
  mutate(illness7 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 7),
         illness14 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 14),
         illness21 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 21)) %>%
  filter(between(Date, as.Date(date) - 27, as.Date(date) + 21)) %>% 
  select(-c(MSA_Code, MSA_Title, Cases, Deaths, Daily_Cases, Daily_Deaths, mean_health))
```

```{r}
city_projection_data
```

```{r}
DT::datatable(city_projection_data, options = list(pageLength = 10))
```

```{r}
city_projection_data <- city_projection_data %>% 
      mutate(R2 = case_when(
        row_number() == 1 ~ city0_model_summary$adj.r.squared,
        row_number() > 1 & row_number() <= 8 ~ city7_model_summary$adj.r.squared,
        row_number() > 8 & row_number() <= 15 ~ city14_model_summary$adj.r.squared,
        row_number() > 15 ~ city21_model_summary$adj.r.squared
      )) %>% 
      mutate(
        Forecast = case_when(
          row_number() == 1 ~ predict(city0_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
          row_number() > 1 & row_number() <= 8 ~ predict(city7_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
          row_number() > 8 & row_number() <= 15 ~ predict(city14_model, 
                                                          newdata = .,
                                                          interval = "prediction", 
                                                          level = 0.95)[, "fit"],
          row_number() > 15 ~ predict(city21_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
          TRUE ~ NA_real_),
        Forecast_Lwr = case_when(
          row_number() == 1 ~ predict(city0_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
          row_number() > 1 & row_number() <= 8 ~ predict(city7_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
          row_number() > 8 & row_number() <= 15 ~ predict(city14_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
          row_number() > 15 ~ predict(city21_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
          TRUE ~ NA_real_
        ),
        Forecast_Upr = case_when(
          row_number() == 1 ~ predict(city0_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
          row_number() > 1 & row_number() <= 8 ~ predict(city7_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
          row_number() > 8 & row_number() <= 15 ~ predict(city14_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
          row_number() > 15 ~ predict(city21_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
          TRUE ~ NA_real_
        )) #%>% 
      #select(Date, MSA_Title, City, Daily_Cases, mean_illness, illness7, illness14, illness21, R2, Forecast_Lwr,
      #       Forecast, Forecast_Upr)
```


```{r}
#city0_model_predict <- lm(Daily_Cases7 ~ mean_illness + illness7 + illness14 + illness21, data = city_projection_data)
#city7_model_predict <- lm(Daily_Cases7 ~ illness7 + illness14 + illness21, data = city_projection_data)
```

These two models result in "0 non-NA cases"
```{r}
city14_model_predict <- lm(Daily_Cases7 ~ illness14 + illness21, data = city_projection_data)
city21_model_predict <- lm(Daily_Cases7 ~ illness21, data = city_projection_data)
```


```{r}
reddit_and_cases %>% 
  filter(City == city) %>%
  mutate(illness7 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 7),
           illness14 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 14),
           illness21 = lag(rollmean(mean_illness, k = 7, align = "right", fill = NA, na.pad = T), n = 21)) %>% 
  filter(between(Date, as.Date(date), as.Date(date) + 21))
```

