---
title: "Complete Analysis"
author: "Rajath Prabhakar"
date: "2024-03-19"
output: html_document
---

```{r}
library(here)
```


##Using the Raw Data

```{r}
source(here("Functions", "02 - combine_reddit().R"))
```
First, the csv file containing Reddit data from all studied cities is loaded into R. Then, this data is cleaned by converting the created_utc column to a date format, removing the created_utc column, and relocating the Date column.

Next, a function called combine_reddit() is defined. It takes a folder path, the aformentioned allcities data frame, and a file name as arguments. Inside the function, for the individual city Reddit data:

    constructs a file path for the specified file name
    Reads the file into a data frame called liwc_df
    Cleans the liwc_df data in an identical manner as the allcities data
    Extracts the city name from the filename
    Filters the allcities data for the corresponding city based on the subreddit column
    Combines the filtered allcities data with the liwc_df data using bind_rows
    Writes the combined data to a new CSV file with the city name and _clean.csv suffix

For example:
combine_reddit("Source Data/01 - Raw", allcities, filename = "liwc22_Atlanta.csv")

```{r}
source(here("Functions", "03 - process_reddit_files().R"))
```

For example:
process_reddit_files(folder_path = "Source Data/02 - Clean Data/", filename = "Atlanta_clean.csv")

