---
title: "Untitled"
author: "Rajath Prabhakar"
date: "2023-08-18"
output: html_document
---
```{r}
library(readxl)
crosswalk <- read_excel("qcew-county-msa-csa-crosswalk.xlsx", sheet = "Feb. 2013 Crosswalk")
crosswalk
```
```{r}
library(dplyr)

# Your existing code to read the data
crosswalk <- read_excel("qcew-county-msa-csa-crosswalk.xlsx", sheet = "Feb. 2013 Crosswalk")
crosswalk <- crosswalk %>% 
  rename(`FIPS` = `County Code`)
crosswalk
write.csv(crosswalk, file = "modified_crosswalk.csv", row.names = FALSE)

```
```{r}
crosswalk <- read.csv("modified_crosswalk.csv")
new_colnames <- gsub("\\.", "_", colnames(crosswalk))
colnames(crosswalk) <- new_colnames
crosswalk
```
```{r}
new_crosswalk <- crosswalk %>% select(c(FIPS, MSA_Code, MSA_Title))
new_crosswalk
```

```{r}
covid_cases <- read.csv("Covid Data/time_series_covid19_confirmed_US.csv")
covid_cases <- covid_cases %>% 
  mutate(across(starts_with("X"), ~ as.numeric(.)))
colnames(covid_cases) <- gsub("^X", "", colnames(covid_cases))
```

```{r}
covid_cases
```

```{r}
cases <- left_join(covid_cases, new_crosswalk, by = "FIPS") %>%
  mutate(across(starts_with("new_crosswalk"), ~ ifelse(is.na(FIPS), "NA", .))) %>% 
  select(UID, iso2, iso3, code3, FIPS, MSA_Code, MSA_Title, everything())
cases
```

```{r}
cases <- cases %>% 
  select(UID, iso2, iso3, code3, FIPS, MSA_Code, MSA_Title, everything())
cases
```

```{r}
cases %>% filter(Province_State == "Georgia")
```
```{r}
covid_deaths <- read.csv("Covid Data/time_series_covid19_deaths_US.csv")
#head(covid_deaths)
covid_deaths <- covid_deaths %>% 
  mutate(across(starts_with("X"), ~ as.numeric(.)))
colnames(covid_deaths) <- gsub("^X", "", colnames(covid_deaths))
covid_deaths
```

```{r}
deaths <- left_join(covid_deaths, new_crosswalk, by = "FIPS") %>%
  mutate(across(starts_with("new_crosswalk"), ~ ifelse(is.na(FIPS), "NA", .))) %>% 
  select(UID, iso2, iso3, code3, FIPS, MSA_Code, MSA_Title, everything())
deaths
```

```{r}
ccf_city_files(folder_path = "DailyData",filename = "Atlanta_daily.csv", explanatory = "mean_i", city = "Atlanta", state = "Georgia", plots = FALSE)
```

```{r}
ccf_city_files(folder_path = "DailyData",filename = "Atlanta_daily.csv", explanatory = "mean_i", city = "Atlanta", state = "Georgia", plots = TRUE)
```

```{r}
ts_city_files(folder_path = "DailyData", filename = "Atlanta_daily.csv", explanatory = "mean_Analytic")
```

```{r}
ccf_city_files(folder_path = "DailyData",filename = "Atlanta_daily.csv", city = "Atlanta", state = "Georgia",plots = FALSE)
```

```{r}
atlanta <- ccf_city_files("DailyData", "Atlanta_daily.csv", city = "Atlanta", state = "Georgia", plots = FALSE)
austin <- ccf_city_files("DailyData", "Austin_daily.csv", city = "Austin", state = "Texas", plots = FALSE)
boston <- ccf_city_files("DailyData", "boston_daily.csv", city = "Boston", state = "Massachusetts", plots = FALSE)
chicago <- ccf_city_files("DailyData", "chicago_daily.csv", city = "Chicago", state = "Illinois", plots = FALSE)
houston <- ccf_city_files("DailyData", "houston_daily.csv", city = "Houston", state = "Texas", plots = FALSE)
LA <- ccf_city_files("DailyData", "LosAngeles_daily.csv", city = "Los Angeles", state = "California", plots = FALSE)
nashville <- ccf_city_files("DailyData", "nashville_daily.csv", city = "Nashville", state = "Tennessee", plots = FALSE)
nyc  <- ccf_city_files("DailyData", "nyc_daily.csv", city = "New York", state = "New York", plots = FALSE)
orlando <- ccf_city_files("DailyData", "orlando_daily.csv", city = "Orlando", state = "Florida", plots = FALSE)

philadelphia <- ccf_city_files("DailyData", "philadelphia_daily.csv", city = "Philadelphia", state = "Pennsylvania", plots = FALSE)

phoenix <- ccf_city_files("DailyData", "phoenix_daily.csv", city = "Phoenix", state = "Arizona", plots = FALSE)
portland <- ccf_city_files("DailyData", "Portland_daily.csv", city = "Portland", state = "Oregon", plots = FALSE)
raleigh <- ccf_city_files("DailyData", "raleigh_daily.csv", city = "Raleigh", state = "North Carolina", plots = FALSE)
san_diego <- ccf_city_files("DailyData", "sandiego_daily.csv", city = "San Diego", state = "California", plots = FALSE)

san_francisco <- ccf_city_files("DailyData", "sanfrancisco_daily.csv", city = "San Francisco", state = "California", plots = FALSE)

seattle <- ccf_city_files("DailyData", "Seattle_daily.csv", city = "Seattle", state = "Washington", plots = FALSE)
stl <- ccf_city_files("DailyData", "StLouis_daily.csv", city = "St. Louis", state = "Missouri", plots = FALSE)
washingtondc <- ccf_city_files("DailyData", "washingtondc_daily.csv", city = "Washington", state = "Maryland", plots = FALSE)
combo <- bind_rows(atlanta, austin, boston, chicago, houston, LA, nashville, nyc, orlando, philadelphia, phoenix, portland, phoenix, portland, raleigh, san_diego, san_francisco, seattle, stl, washingtondc) %>% 
  select(City, State, Variable, Max_ACF, Lag)
combo
fwrite(combo, paste("combined_data.csv"))

```

```{r}
combined <- read_csv("combined_data.csv")
combined
```
```{r}
combined_negative <- combined %>% filter(Lag <= 0) %>%
  group_by(Variable) %>% 
  summarize(Average_ACF_negative = mean(Max_ACF),
            Average_Lag_negative = mean(Lag))
combined_negative
```

```{r}
combined_positive <- combined %>% filter(Lag > 0) %>%
  group_by(Variable) %>% 
  summarize(Average_ACF_positive = mean(Max_ACF),
            Average_Lag_positive = mean(Lag))
combined_positive
```
```{r}
table1 <- left_join(combined_positive, combined_negative, by = "Variable")
fwrite(table1, paste("table_of_average_acf_lag.csv"))
```

```{r}
combined <- read_csv("combined_data.csv")
city_list <- split(combined, combined$City)
for (city_name in names(city_list)) {
  assign(city_name, city_list[[city_name]])
}
```

```{r}
assign("Los_Angeles", `Los Angeles`)
assign("San_Francisco", `San Francisco`)
assign("San_Diego", `San Diego`)
assign("stl", `St. Louis`)
assign("NYC", `New York`)
```

Atlanta
```{r}
atlanta_rank_negative <- Atlanta %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
atlanta_rank_positive <- Atlanta %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
atlanta_rank <- left_join(atlanta_rank_positive, atlanta_rank_negative, by = "Variable")
atlanta_rank <- atlanta_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
 
```
positive: mean_emo_sad
negative: mean_Analytic

Austin
```{r}
austin_rank_negative <- Austin %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
austin_rank_positive <- Austin %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
austin_rank <- left_join(austin_rank_positive, austin_rank_negative, by = "Variable")
austin_rank <- austin_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_health
negative: mean_emo_anger

Boston
```{r}
boston_rank_negative <- Boston %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
boston_rank_positive <- Boston %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
boston_rank <- left_join(boston_rank_positive, boston_rank_negative, by = "Variable")
boston_rank <- boston_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_illness
negative: mean_illness

Chicago
```{r}
chicago_rank_negative <- Chicago %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
chicago_rank_positive <- Chicago %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
chicago_rank <- left_join(chicago_rank_positive, chicago_rank_negative, by = "Variable")
chicago_rank <- chicago_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_family
negative: mean_family

Houston
```{r}
houston_rank_negative <- Houston %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
houston_rank_positive <- Houston %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
houston_rank <- left_join(houston_rank_positive, houston_rank_negative, by = "Variable")
houston_rank <- houston_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
Positive: mean_illness
Negative: mean_illness

Los Angeles
```{r}
LA_rank_negative <- Los_Angeles %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
LA_rank_positive <- Los_Angeles %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
LA_rank <- left_join(LA_rank_positive, LA_rank_negative, by = "Variable")
LA_rank <- LA_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
Positive: mean_family
Negative: mean_tentat

Nashville 
```{r}
nashville_rank_negative <- Nashville %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
nashville_rank_positive <- Nashville %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
nashville_rank <- left_join(nashville_rank_positive, nashville_rank_negative, by = "Variable")
nashville_rank <- nashville_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```

Positive: mean_ppron
Negative: mean_emo_pos

New York
```{r}
nyc_rank_negative <- NYC %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
nyc_rank_positive <- NYC %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
nyc_rank <- left_join(nyc_rank_positive, nyc_rank_negative, by = "Variable")
nyc_rank <- nyc_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
Positive: mean_illness
Negative: mean_mental

Orlando
```{r}
orlando_rank_negative <- Orlando %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
orlando_rank_positive <- Orlando %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
orlando_rank <- left_join(orlando_rank_positive, orlando_rank_negative, by = "Variable")
orlando_rank <- orlando_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_illness
negative: mean_emo_anger

Philadelphia
```{r}
PHI_rank_negative <- Philadelphia %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
PHI_rank_positive <- Philadelphia %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
PHI_rank <- left_join(PHI_rank_positive, PHI_rank_negative, by = "Variable")
PHI_rank <- PHI_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_fatigue
negative: mean_Tone

Phoenix
```{r}
Phoenix <- Phoenix %>% 
  slice(1:100)
PHX_rank_negative <- Phoenix %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
PHX_rank_positive <- Phoenix %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
PHX_rank <- left_join(PHX_rank_positive, PHX_rank_negative, by = "Variable")
PHX_rank <- PHX_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_tone_pos
negative: mean_Tone

Portland
```{r}
Portland <- Portland %>% 
  slice(1:100)
portland_rank_negative <- Portland %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
portland_rank_positive <- Portland %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
portland_rank <- left_join(portland_rank_positive, portland_rank_negative, by = "Variable")
portland_rank <- portland_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)
```
positive: mean_tone_pos
negative: mean_ipron

Raleigh

```{r}
raleigh_rank_negative <- Raleigh %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
raleigh_rank_positive <- Raleigh %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
raleigh_rank <- left_join(raleigh_rank_positive, raleigh_rank_negative, by = "Variable")
raleigh_rank <- raleigh_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_Analytic
negative: mean_Analytic

San Diego
```{r}
sd_rank_negative <- San_Diego %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
sd_rank_positive <- San_Diego %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
sd_rank <- left_join(sd_rank_positive, sd_rank_negative, by = "Variable")
sd_rank <- sd_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_affiliation
negative: mean_affiliation

San Francisco
```{r}
sf_rank_negative <- San_Francisco %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
sf_rank_positive <- San_Francisco %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
sf_rank <- left_join(sf_rank_positive, sf_rank_negative, by = "Variable")
sf_rank <- sf_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_Tone
negative: mean_Social

Seattle
```{r}
seattle_rank_negative <- Seattle %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
seattle_rank_positive <- Seattle %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
seattle_rank <- left_join(seattle_rank_positive, seattle_rank_negative, by = "Variable")
seattle_rank <- seattle_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_ipron
negative: mean_mental

St. Louis
```{r}
stl_rank_negative <- stl %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
stl_rank_positive <- stl %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
stl_rank <- left_join(stl_rank_positive, stl_rank_negative, by = "Variable")
stl_rank <- stl_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_fatigue
negative: mean_Analytic

Washington DC
```{r}
washington_rank_negative <- Washington %>% 
  filter(Lag <= 0) %>% 
  mutate(Negative_Lag_Rank = rank(-abs(Max_ACF))) 
  
washington_rank_positive <- Washington %>% 
  filter(Lag > 0) %>% 
  mutate(Positive_Lag_Rank = rank(-abs(Max_ACF))) 
washington_rank <- left_join(washington_rank_positive, washington_rank_negative, by = "Variable")
washington_rank <- washington_rank %>% 
  select(-c(City.y, State.y)) %>% 
  rename(City = City.x,
         State = State.x,
         Max_ACF_Positive = Max_ACF.x,
         Lag_Positive = Lag.x,
         Max_ACF_Negative = Max_ACF.y,
         Lag_Negative = Lag.y)

```
positive: mean_illness
negative: mean_illness

```{r}
combined_ranks <- bind_rows(atlanta_rank, austin_rank, boston_rank, 
                            chicago_rank, houston_rank, LA_rank, nashville_rank, 
                            nyc_rank, orlando_rank, PHI_rank, PHX_rank, portland_rank,
                            raleigh_rank,sd_rank, sf_rank, seattle_rank, stl_rank, washington_rank)
```

```{r}
rank_avg <- combined_ranks %>% 
  group_by(Variable) %>% 
  summarize(avg_rank_pos = mean(Positive_Lag_Rank),
            avg_rank_neg = mean(Negative_Lag_Rank))
fwrite(rank_avg, paste("Average_City_Rank.csv"))
```

```{r}
rank_avg
```

```{r}
library(maps)
usa <- map_data("usa")
states <- map_data("state")


```

```{r}
ggplot(states, aes(long, lat, group = group)) + 
  geom_polygon(fill = "gray90", color = "gray50") + 
  coord_map("mercator") + 
  ggtitle("USA") + 
  theme_void()
```
```{r}
indicators <- unique(combined_ranks$Variable)
#states <- states %>% rename(State = region)
states$region <- str_to_title(states$State)

merged_data <- merge(states, combined_ranks, by.x = "region", by.y = "State", all.x = TRUE)

# Plot the map with state boundaries and fill colors based on the top-ranked indicator
ggplot(merged_data, aes(x = long, y = lat, group = group, fill = Variable)) +
  geom_polygon(color = "gray50") +
  coord_map("mercator") +
  ggtitle("USA with State Boundaries Colored by Top-Ranked Indicator") +
  theme_void() +
  scale_fill_manual(values = indicators)
```
```{r}
rank <- read_csv("Average_City_Rank.csv")
rank
```
```{r}
rank_subset <- rank %>% arrange((abs(avg_rank_pos)))
rank_subset <- head(rank_subset, 15)
ggplot(rank, aes(x = reorder(Variable, -avg_rank_pos), y = avg_rank_pos, fill = Variable)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 15 Variables by Average Rank (Positive Lags)",
       x = "Variable",
       y = "Average Rank")+
  coord_flip()+
  theme(axis.text.y = element_text(angle = 0, size = 8))+
  guides(fill = FALSE)
```
```{r}
avg_acf_lag <- read_csv("table_of_average_acf_lag.csv")
```
```{r}
combined <- read_csv("combined_data.csv")
```
Here I am filtering mean_illness because it has the highest average rank for positive lags. 
```{r}
illness <- combined %>% 
  filter(Variable == "mean_illness" & Lag > 0)
health <- combined %>% 
  filter(Variable == "mean_health" & Lag > 0) 
```

```{r}
ggplot(illness, aes(x = Lag, y = Max_ACF))+
  geom_point()
```
```{r}
ggplot(health, aes(x = Lag, y = Max_ACF))+
  geom_point()
```
```{r}
combined_positive <- combined %>% 
  filter(Lag > 0)
ggplot(combined_positive, aes(x = Lag, y = Max_ACF))+
  geom_point()
```

```{r}
covid_cases
```

