---
title: "CCF Plots"
author: "Rajath Prabhakar"
date: "2023-11-12"
output: html_document
---
```{r}
library(here)
```

```{r}
source(here::here("Results/ccf_city_case_files().R"))
```
**Atlanta**
***Health***
```{r}
ccf_city_case_files("Results/Daily Data", "atlanta_daily.csv", explanatory = "mean_health", code = "C1206", city = "Atlanta", state = "Georgia", plots = TRUE, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "atlanta_daily.csv", explanatory = "mean_illness", code = "C1206", city = "Atlanta", state = "Georgia", plots = TRUE, lags = "both")
```


**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "atlanta_daily.csv", explanatory = "mean_emo_anx", code = "C1206", city = "Atlanta", state = "Georgia", plots = TRUE, lags = "both")
```


*Austin*

**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "austin_daily.csv", explanatory = "mean_health", code = "C1242", city = "Austin", state = "Texas", plots = TRUE, lags = "both")
```


**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "austin_daily.csv", explanatory = "mean_illness", code = "C1242", city = "Austin", state = "Texas", plots = TRUE, lags = "both")
```


**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "austin_daily.csv", explanatory = "mean_emo_anx", code = "C1242", city = "Austin", state = "Texas", plots = TRUE, lags = "both")
```


*Boston*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "boston_daily.csv", explanatory = "mean_health", code = "C1446", city = "Boston", state = "Massachusetts", plots = TRUE, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "boston_daily.csv", explanatory = "mean_illness", code = "C1446", city = "Boston", state = "Massachusetts", plots = TRUE, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "boston_daily.csv", explanatory = "mean_emo_anx", code = "C1446", city = "Boston", state = "Massachusetts", plots = TRUE, lags = "both")
```

*Chicago*

**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "chicago_daily.csv",explanatory = "mean_health", code = "C1698", city = "Chicago", state = "Illinois", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "chicago_daily.csv",explanatory = "mean_illness", code = "C1698", city = "Chicago", state = "Illinois", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "chicago_daily.csv",explanatory = "mean_emo_anx", code = "C1698", city = "Chicago", state = "Illinois", plots = T, lags = "both")
```

*Houston*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "houston_daily.csv", explanatory = "mean_health", code = "C2642", city = "Houston", state = "Texas", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "houston_daily.csv", explanatory = "mean_illness", code = "C2642", city = "Houston", state = "Texas", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "houston_daily.csv", explanatory = "mean_emo_anx", code = "C2642", city = "Houston", state = "Texas", plots = T, lags = "both")
```

*LA*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "losangeles_daily.csv", explanatory = "mean_health", code = "C3108", city = "Los Angeles", state = "California", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "losangeles_daily.csv", explanatory = "mean_illness", code = "C3108", city = "Los Angeles", state = "California", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "losangeles_daily.csv", explanatory = "mean_emo_anx", code = "C3108", city = "Los Angeles", state = "California", plots = T, lags = "both")
```

*Nashville*
**Health**
```{r}
nashville <- ccf_city_case_files("Results/Daily Data", "nashville_daily.csv", explanatory = "mean_health", code = "C3498", city = "Nashville", state = "Tennessee", plots = T, lags = "both")
```

**Illness**
```{r}
nashville <- ccf_city_case_files("Results/Daily Data", "nashville_daily.csv", explanatory = "mean_illness", code = "C3498", city = "Nashville", state = "Tennessee", plots = T, lags = "both")
```

**Anxiety**
```{r}
nashville <- ccf_city_case_files("Results/Daily Data", "nashville_daily.csv", explanatory = "mean_emo_anx", code = "C3498", city = "Nashville", state = "Tennessee", plots = T, lags = "both")
```


*NYC*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "nyc_daily.csv", explanatory = "mean_health", code = "C3562", city = "New York", state = "New York", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "nyc_daily.csv", explanatory = "mean_illness", code = "C3562", city = "New York", state = "New York", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "nyc_daily.csv", explanatory = "mean_emo_anx", code = "C3562", city = "New York", state = "New York", plots = T, lags = "both")
```


*Orlando*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "orlando_daily.csv", explanatory = "mean_health", code = "C3674", city = "Orlando", state = "Florida", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "orlando_daily.csv", explanatory = "mean_illness", code = "C3674", city = "Orlando", state = "Florida", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "orlando_daily.csv", explanatory = "mean_emo_anx", code = "C3674", city = "Orlando", state = "Florida", plots = T, lags = "both")
```


*Philadelphia*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "philadelphia_daily.csv", explanatory = "mean_health", code = "C3798", city = "Philadelphia", state = "Pennsylvania", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "philadelphia_daily.csv", explanatory = "mean_illness", code = "C3798", city = "Philadelphia", state = "Pennsylvania", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "philadelphia_daily.csv", explanatory = "mean_emo_anx", code = "C3798", city = "Philadelphia", state = "Pennsylvania", plots = T, lags = "both")
```


*Phoenix*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "phoenix_daily.csv", explanatory = "mean_health", code = "C3806", city = "Phoenix", state = "Arizona", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "phoenix_daily.csv", explanatory = "mean_illness", code = "C3806", city = "Phoenix", state = "Arizona", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "phoenix_daily.csv", explanatory = "mean_emo_anx", code = "C3806", city = "Phoenix", state = "Arizona", plots = T, lags = "both")
```


*Portland*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "portland_daily.csv", explanatory = "mean_health", code = "C3890", city = "Portland", state = "Oregon", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "portland_daily.csv", explanatory = "mean_illness", code = "C3890", city = "Portland", state = "Oregon", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "portland_daily.csv", explanatory = "mean_emo_anx", code = "C3890", city = "Portland", state = "Oregon", plots = T, lags = "both")
```


*Raleigh*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "raleigh_daily.csv", explanatory = "mean_health", code = "C3958", city = "Raleigh", state = "North Carolina", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "raleigh_daily.csv", explanatory = "mean_illness", code = "C3958", city = "Raleigh", state = "North Carolina", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "raleigh_daily.csv", explanatory = "mean_emo_anx", code = "C3958", city = "Raleigh", state = "North Carolina", plots = T, lags = "both")
```


*San Diego*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "sandiego_daily.csv", explanatory = "mean_health", code = "C4174", city = "San Diego", state = "California", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "sandiego_daily.csv", explanatory = "mean_illness", code = "C4174", city = "San Diego", state = "California", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "sandiego_daily.csv", explanatory = "mean_emo_anx", code = "C4174", city = "San Diego", state = "California", plots = T, lags = "both")
```


*San Francisco*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "sanfrancisco_daily.csv",explanatory = "mean_health", code = "C4186", city = "San Francisco", state = "California", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "sanfrancisco_daily.csv",explanatory = "mean_illness", code = "C4186", city = "San Francisco", state = "California", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "sanfrancisco_daily.csv",explanatory = "mean_emo_anx", code = "C4186", city = "San Francisco", state = "California", plots = T, lags = "both")
```


*Seattle*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "seattle_daily.csv",explanatory = "mean_health", code = "C4266", city = "Seattle", state = "Washington", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "seattle_daily.csv",explanatory = "mean_illness", code = "C4266", city = "Seattle", state = "Washington", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "seattle_daily.csv",explanatory = "mean_emo_anx", code = "C4266", city = "Seattle", state = "Washington", plots = T, lags = "both")
```


*St. Louis*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "stlouis_daily.csv",explanatory = "mean_health",code = "C4118", city = "St. Louis", state = "Missouri", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "stlouis_daily.csv",explanatory = "mean_illness",code = "C4118", city = "St. Louis", state = "Missouri", plots = T, lags = "both")
```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "stlouis_daily.csv",explanatory = "mean_emo_anx",code = "C4118", city = "St. Louis", state = "Missouri", plots = T, lags = "both")
```


*Washington*
**Health**
```{r}
ccf_city_case_files("Results/Daily Data", "washingtondc_daily.csv", explanatory = "mean_health",code = "C4790", city = "Washington", state = "Maryland", plots = T, lags = "both")
```

**Illness**
```{r}
ccf_city_case_files("Results/Daily Data", "washingtondc_daily.csv", explanatory = "mean_illness",code = "C4790", city = "Washington", state = "Maryland", plots = T, lags = "both")

```

**Anxiety**
```{r}
ccf_city_case_files("Results/Daily Data", "washingtondc_daily.csv", explanatory = "mean_emo_anx",code = "C4790", city = "Washington", state = "Maryland", plots = T, lags = "both")

```


