---
title: "Model Code"
author: "Rajath Prabhakar"
date: "2023-12-06"
output: html_document
---
```{r}
library(tidyverse)
library(here)
library(zoo)
library(data.table)
```

```{r}
#reddit_and_cases <- read_csv(here("Results/CSV Files/reddit_and_cases_deaths.csv"))
```

```{r}
reddit_and_cases <- read_csv("C:/Users/14049/Desktop/Reddit-Forecasting-Project/Results/CSV Files/reddit_and_cases_deaths.csv")
```

```{r}
library(MASS)
model <- lm(Daily_Cases7 ~ mean_health*mean_illness, data = reddit_and_cases)
summary(model)
```
```{r}
library(MMWRweek)
library(tidyr)
reddit_and_cases1 <- reddit_and_cases %>%
  group_by(MSA_Code) %>% 
  mutate(MMWR_Date = MMWRweek(Date), 
         Cases_Lag7 = lag(Daily_Cases, n = 7),
         Cases_Lag14 = lag(Daily_Cases, n = 14),
         Cases_Lag21 = lag(Daily_Cases, n = 21)) %>%
  unnest_wider(MMWR_Date) %>% 
  na.omit() #%>% 
#reddit_and_cases1 <- reddit_and_cases1 %>% 
#  select(Date, MMWRyear, MMWRweek, MMWRday, Daily_Cases, Cases_Lag7, Cases_Lag14, Cases_Lag21, everything())
```

use reddit data (specifically illness indicator) to predict cases for the next week
Lag case data by 1 or 2 weeks (do this in dataset first, then model it)

```{r}
covid_model <- lm(Daily_Cases ~ Cases_Lag7 + Cases_Lag14 + Cases_Lag21 + MMWRweek + MMWRday, data = reddit_and_cases1)
summary(covid_model)
plot(covid_model)
```
Lagging renders day of week effect not significant. 
```{r}
reddit_and_cases2 <- reddit_and_cases1 %>%
  ungroup() %>% 
  #group_by(MSA_Code) %>% 
  mutate(predicted_Daily_Cases = predict(covid_model))
```

```{r}
ggplot(reddit_and_cases2 %>% filter(MSA_Code == "C1206") %>% filter(Date >= "2020-03-01" & Date <= "2021-12-01"), aes(x = Date))+
  geom_line(aes(y = predicted_Daily_Cases))+
  geom_line(aes(y = Daily_Cases), color = "red")
```

covid_model1 
- remove data before March 1, 2020 and after June 1, 2021 (Before Delta Variant)
- linear regression with and without Reddit coefficient

```{r}
reddit_and_cases3 <- reddit_and_cases1 %>% filter(Date >= "2020-03-01" & Date <= "2021-06-01") %>% 
  group_by(MSA_Code) %>% 
  mutate(illness7 = lag(mean_illness, n =7),
         illness14 = lag(mean_illness, n = 14), 
         illness21 = lag(mean_illness, n = 21)) %>% 
  na.omit()

```

```{r}
covid_model1 <- lm(Daily_Cases ~ Cases_Lag7 + Cases_Lag14 + Cases_Lag21 + illness7 + illness14 + illness21 + MMWRweek, 
                   data = reddit_and_cases3)
summary(covid_model1)
```
```{r}
covid_model2 <- lm(Daily_Cases ~ Cases_Lag7 + Cases_Lag14 + Cases_Lag21 + MMWRweek, data = reddit_and_cases3)
summary(covid_model2)
```
```{r}

```

```{r}
covid_model3 <- lm(Daily_Cases ~ illness7 + illness14 + illness21, data = reddit_and_cases3)
summary(covid_model3)
```
 
- maybe negbinom? 
```{r}
reddit_and_cases4 <- reddit_and_cases1 %>% filter(Date >= "2020-03-01" & Date <= "2021-06-01") %>%
  filter(Daily_Cases >= 0) %>% 
  group_by(MSA_Code) %>% 
  mutate(illness7 = lag(mean_illness, n =7),
         illness14 = lag(mean_illness, n = 14), 
         illness21 = lag(mean_illness, n = 21)) %>% 
  na.omit()
```

```{r}
covid_model4 <- glm(Daily_Cases ~ Cases_Lag7 + illness7 + MMWRweek, family = "poisson", data = reddit_and_cases4)
summary(covid_model4)
```
comparison of residual to null
see whether the prediction matches the actual data

plot fitted values
```{r}
plot(covid_model4)
```

Model 1: flu(today) = flu(yest) + 
raw case counts should be response variable, illness should be explanatory

WRT Covid
Covid Case counts today predicted by linear regression based on covid case counts of previous two weeks, day of week effect, epiweek

Then add in Reddit data 

1. Take dataframe, lag columns to create lagged covid cases from 7, 14, and 21 days ago. 

cases_lag7
cases_lag14
cases_lag21

2. these columns go in lm()



```{r}
library(conflicted)
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("between", "dplyr")
forecasting_data_atlanta <- reddit_and_cases %>%
  mutate(illness7 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 7),
         illness14 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 14),
         illness21 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 21)) %>% 
  filter(between(Date, as.Date("2021-05-01") - 28, as.Date("2021-05-01")) & MSA_Code == "C1206") %>%
  select(Date, City, MSA_Code, Daily_Cases7, mean_illness, illness7, illness14, illness21) %>% 
  na.omit()
```

Atlanta 7-day forecast
```{r}
atlanta7_model <- lm(Daily_Cases7 ~ illness7 + illness14 + illness21, data = forecasting_data_atlanta)
atlanta7_model_summary <- summary(atlanta7_model)
atlanta7_model_summary
```
Filtering from 5/1/2020 - 28 days resulted in a much lower R2 compared to filtering from 5/1/2021 - 28 days (0.098 compared to 0.75 ish). Suggests that as the pandemic went on, the forecast gets better?


Atlanta 14-day forecast
```{r}
atlanta14_model <- lm(Daily_Cases7 ~ illness14 + illness21, data = forecasting_data_atlanta)
atlanta14_model_summary <- summary(atlanta14_model)
atlanta14_model_summary
```

Atlanta 21-day forecast
```{r}
atlanta21_model <- lm(Daily_Cases7 ~ illness21, data = forecasting_data_atlanta)
atlanta21_model_summary <- summary(atlanta21_model)
atlanta21_model_summary
```
```{r}
forecasting_data_atlanta1 <- reddit_and_cases %>%
  filter(MSA_Code == "C1206") %>%
  mutate(illness7 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 7),
         illness14 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 14),
         illness21 = lag(rollmeanr(mean_illness, k = 7, fill = NA), n = 21)) %>%
  na.omit() %>%
  filter(between(Date, as.Date("2021-05-01"), as.Date("2021-05-01") + 21)) %>% 
  mutate(R2_7 = atlanta7_model_summary$adj.r.squared,
         R2_14 = atlanta14_model_summary$adj.r.squared,
         R2_21 = atlanta21_model_summary$adj.r.squared) %>%
  mutate(Forecast = case_when(
      row_number() <= 7 ~ predict(atlanta7_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
      row_number() > 7 & row_number() <= 14 ~ predict(atlanta14_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
      row_number() > 14 ~ predict(atlanta21_model, newdata = ., interval = "prediction", level = 0.95)[, "fit"],
      TRUE ~ NA_real_
    ),
    Forecast_Lwr = case_when(
      row_number() <= 7 ~ predict(atlanta7_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
      row_number() > 7 & row_number() <= 14 ~ predict(atlanta14_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
      row_number() > 14 ~ predict(atlanta21_model, newdata = ., interval = "prediction", level = 0.95)[, "lwr"],
      TRUE ~ NA_real_
    ),
    Forecast_Upr = case_when(
      row_number() <= 7 ~ predict(atlanta7_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
      row_number() > 7 & row_number() <= 14 ~ predict(atlanta14_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
      row_number() > 14 ~ predict(atlanta21_model, newdata = ., interval = "prediction", level = 0.95)[, "upr"],
      TRUE ~ NA_real_
    )) %>% 
  select(-c(2, 4:7, 9:12))

fwrite(forecasting_data_atlanta1, paste("C:/Users/14049/Desktop/Reddit-Forecasting-Project/Results/CSV Files/forecasting_data_Atlanta_2021_05_01.csv"))
```

For loop for 7 day forecast for Atlanta
```{r}
atlanta_cases <- reddit_and_cases %>% 
  filter(MSA_Code == "C1206") %>% 
  filter(Date >= "2020-05-01")
atlanta_df <- data.frame()
for (i in atlanta_cases$Date) {
  atlanta1 <- atlanta_cases %>%
    mutate(illness7 = lag(rollmean(mean_illness, k = 7, fill = NA), n = 7),
         illness14 = lag(rollmean(mean_illness, k = 7, fill = NA), n = 14),
         illness21 = lag(rollmean(mean_illness, k = 7, fill = NA), n = 21)) %>% 
    filter(between(Date, as.Date(i), as.Date(i) + 28)) #%>%
#    select(Date, City, MSA_Code, Daily_Cases7, mean_illness, illness7, illness14, illness21) %>%
#    na.omit()
#  model <- lm(Daily_Cases7 ~ illness7 + illness14 + illness21, data = atlanta_cases)
#  forecasting_data_atlanta7 <- atlanta_cases %>% 
#    mutate(Forecast7 = predict(model)) %>%
#    na.omit()
  
}
```

What above code is supposed to do: I have a a filtered dataset (atlanta_cases) from reddit_and_cases that filters only for Atlanta MSA and Date starting from 4/3/2020. In the for loop, I have a new object forecasting_data_atlanta1 that takes atlanta_cases, adds columns illness 7, 14, and 21, filters only for the date and 28 days after, and selects the columns above. With this data,  

```{r}
forecast_reddit(date = "2021-05-01", city = "Atlanta")
```

